Proposed Solution

### 2017-01-22 CAV17/secs/learner.tex
small stuff
add definitions to post-analysis section
and comment hook for \rahul{}

@@

\para{Integer Correlation}
\app supports two types of integer correlation rules, coarse-grained and fine-grained.
Coarse-grained rules follow $X \implies compare(X,Y)$, where $|X|,|Y|=1$ and $compare \in \{<,=,>\}$, such that $X$ must hold $compare$ to $Y$.
Fine-grained rules follow $X \implies compare(X,Y)$, where $|X|=2,|Y|=1$ and $compare \in \{<,=,>\}$, such that for $k_1,\ k_2 \in X,\ k1*k2$ must hold $compare$ to $Y$.
These rules also implement a typing judgment over the keywords probabilistic type.
To avoid learning too many false positives, we restrict this rule to either $size*int=size$, $int*size=size$, or $int*int = int$.
Without probabilistic typing, we would also learn, for example, $int*int=size$.
%TODO Aaron

@@

\app is primarily implemented in Haskell, with a bit of mongo.
The translator is developed as a parser for the grammar described in $\S$\ref{sec-trans}. 
The learner and checker module fully implemented the design in $\S$\ref{sec-learn} and $\S$\ref{sec-checker}, respectively.

The source code for our implementation is available at {\em (URL omitted for blind review)}.

>>>>

\rahul{and we may even be able to say that these insidiuous issues are much
harder to pin down by the standard delta-debugging technique of starting a
system multiple times with different configuration settings}

@@

\para{Integer Correlation}
\app supports two types of integer correlation rules, coarse-grained and fine-grained.
Coarse-grained rules follow $X \implies compare(X,Y)$, where $|X|,|Y|=1$ and $compare \in \{<,=,>\}$, such that $X$ must hold $compare$ to $Y$.
Fine-grained rules follow $X \implies compare(X,Y)$, where $|X|=2,|Y|=1$ and $compare \in \{<,=,>\}$, such that for $k_1,\ k_2 \in X,\ k1*k2$ must hold $compare$ to $Y$.
These rules also implement a typing judgment over the keywords probabilistic type.
To avoid learning too many false positives, we restrict this rule to either $size*int=size$, $int*size=size$, or $int*int = int$.
Without probabilistic typing, we would also learn, for example, $int*int=size$.
%TODO include exactly how many false positive we prune with types over our training set? Here or in eval?

%TODO Aaron - add to learinign module section describe implemetnation?

\app is primarily implemented in Haskell.
The source code for our implementation is available at {\em (URL omitted for blind review)}.

@@

### 2017-01-22 CAV17/secs/postanal.tex
add definitions to post-analysis section
and comment hook for \rahul{}

Define a graph with labeled, weighted edges $G = (V,E)$ such that:
\iffalse
    V \def { keywords }

Where

    E \def { (v_1, v_2, l, w) }
\fi

Where the label $l$ defines the relationship, and the weight $w$ is
defined as $w = \frac{true - false}{total}$ for that relationship.
Note that due to support / confidence assertions in the learner, we
may be assured that all weights in the graph are positive.

\para {Definition}
Degree (in-degree + out-degree) for each node

Define in-degree and out-degree in the usual way:

\iffalse    IN_DEGREE(k) = ||

    $\forall keyword k \in rules, in\_degree()$
\fi

>>>>

Define a graph with labeled, weighted edges $G = (V,E)$ such that:

    $$V = \{ keywords \}$$

and

    $$E = \{ (v_1, v_2, l, w) \}$$

Where the label $l \in L$ indicates the predicate $p$ extracted by the learner,
$L$ is the set of all predicates learned,
and the weight $w$ is defined as

    $$w = \frac{true - false}{total}$$

for that relationship. For notational convenience later in this section
we will refer to $w_{v_1, v_2, l}$ as referring to the weight of the
edge $(v_1, v_2, l, w)$. We will refer to this graph as the {\bf Rule Graph}
in further analysis.

Note that due to support / confidence assertions in the learner, we
may be assured that all weights in the graph are positive.

\para {Definition}
We define a measure of degree for each node as the sum of in-degree
and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:

    $$DEGREE(x) = OUT\_DEGREE(x) + IN\_DEGREE(x)$$

    $$DEGREE(x) = \sum_{l \in L} \sum_{v \in V} w_{x, v, l} + \sum_{l \in L} \sum_{v \in V} w_{v, x, l}$$

The more rules of high confidence extracted for a keyword by the learner, 
the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
We may use this measurement to examine which keywords in the configuration
space examined by the learner are most important - which keyword configurations
are the most constrained / most constraining.
